Choosing and rating harmonies

### 2020-08-14 simulations_MMPD6.Rmd
initial commit
cleaner code

@@

```{r diffnull_3levels}

@@

>>>>

# Levels and Power of the test statistic

@@

<!-- ```{r diffnull_3levels} -->

<!-- ``` -->

@@

# Permutation test

To estimate the sampling distribution of the test statistic we
need many samples generated under the null hypothesis.
If the null hypothesis is true, changing the exposure would have
no effect on the outcome. By randomly shuffling the exposures
we can make up as many data sets as we like.
If the null hypothesis is true the shuffled data sets should look
like the real data, otherwise they should look different from the
real data.
The ranking of the real test statistic among the shuffled test
statistics gives a p-value.

```{r}
harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2))

har1 <- harmonies[1,]

sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2))

data1 <- sim_distharmony1(har1, sim_dist = sim_dist1)
data1

data1 %>% unnest(sim_dist) %>%
  ggplot(aes(x = Var2, y = sim_dist)) +
  facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3")

response = "sim_dist"

MMPD_distribution <- data1 %>%
  select(-dist) %>% 
  unnest(sim_dist) %>% 
  list() %>% 
  global_threshold(harmony_tbl = har1,
                   response = "sim_dist",
                   dist_distribution = "normal",
                   dist_ordered = TRUE,
                   create_gran_data = FALSE, nsamp = 20)

# as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>% 
#   ggplot() + geom_histogram(aes(x = value))
